\Large \bf Conjure: Summoning Proxies from Unused Address Space

### 2019-05-15 paper/figures.tex
update application overview fig

\newcommand{\FigOverview}{
\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth,clip]{figures/dark-decoy-overview.png}
    \caption{\textbf{\scheme Operations}\,---\,%
        Clients first register by sending a secret seed in a steganographic tag past the station in a
        normal TLS connection to a Decoy site. Clients then connect to an address derived from the seed,
        which the station responds as a phantom host. If the client can prove knowledge of the
        seed used during registration, they are allowed access to the proxy. Otherwise,
        their traffic is forwarded to a Mask Site to make it difficult for censors to distinguish
        phantom hosts from legitimate ones.
    }
    \label{fig:overview}
\end{figure}
}

\newcommand{\FigHighLevel}{
\begin{figure}[t]
    \centering
    \vspace{-0.54in}
    \includegraphics[width=\linewidth,clip]{figures/high-level.png}
    \caption{\textbf{\scheme Overview}---%
      An ISP deploys a \scheme station, which sees a passive tap of passing traffic.
      Following a steganographic registration process, a client can connect
      to an unused IP address in the ISP's AS, and the station will
      inject packets to communicate with the client as if there were a proxy server at that address.
    }
    \label{fig:highlevel}
\end{figure}
}

>>>>

\newcommand{\FigOverview}{
\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth,clip]{figures/conjure-overview.png}
    \caption{\textbf{\scheme Operations}\,---\,%
        Clients first register by sending a secret seed in a steganographic tag past the station in a
        normal TLS connection to a Decoy site. Clients then connect to an address derived from the seed,
        which the station responds as a phantom host application. If the client can prove knowledge of the
        seed used during registration, they are allowed access to the proxy. Otherwise,
        the phantom host application pretends to be a benign host by staying silent or forwarding traffic
        to a mask site to make it difficult for censors to distinguish phantom hosts from legitimate ones.
    }
    \label{fig:overview}
\end{figure}
}

\newcommand{\FigHighLevel}{
\begin{figure}[]
    \centering
    %\vspace{-0.54in}
    \includegraphics[width=\linewidth,clip]{figures/high-level.png}
    \caption{\textbf{\scheme Overview}---%
      An ISP deploys a \scheme station, which sees a passive tap of passing traffic.
      Following a steganographic registration process, a client can connect
      to an unused IP address in the ISP's AS, and the station will
      inject packets to communicate with the client as if there were a proxy server at that address.
    }
    \label{fig:highlevel}
\end{figure}
}
